Analyzing Geographic and Demographic Patterns of Homelessness

### 2024-01-23 outputs/paper/paper.qmd
major updates on scripts and modified some files

---
title: "Analyzing Geographic and Demographic Patterns of Homelessness"
subtitle: "Exploring Spatial Variations in Shelter Demand and Gender/Age-Based Disparities"
author: 
  - Jiwon Choi
thanks: "Code and data are available at [github.com/putrepohere](https://github.com/jmacattack27/ModellingHomelessPopulations)."
date: today
date-format: long
abstract: "This study examines the challenges faced by the homeless despite the presence of shelters, triggered by a recent incident of a homeless person succumbing to severe cold. It investigates geographic and demographic trends in homelessness, analyzing variations in shelter demand based on location and gender/age disparities. Utilizing data from the Shelter Support and Housing Administration division's Shelter Management Information System database, the research forecasts demand and provides critical insights: (1) geographic analysis identifies areas with the highest demand for shelter services, (2) demographic analysis uncovers gender and age-based disparities. These insights empower policymakers, shelter providers, and advocacy groups to allocate resources efficiently and proactively address homelessness challenges, ultimately preventing future hardships and tragedies."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
```

>>>>

---
title: "Analyzing Geographic and Demographic Patterns of Homelessness"
subtitle: "Exploring Spatial Variations in Shelter Demand and Gender/Age-Based Disparities"
author: 
  - Jiwon Choi
thanks: "Code and data are available at: [https://github.com/jwonc4602/Analyzing-Geographic-and-Demographic-Patterns-of-Homelessness](https://github.com/jwonc4602/Analyzing-Geographic-and-Demographic-Patterns-of-Homelessness)."
date: today
date-format: long
abstract: "This study examines the challenges faced by the homeless despite the presence of shelters, triggered by a recent incident of a homeless person succumbing to severe cold. It investigates geographic and demographic trends in homelessness, analyzing variations in shelter demand based on location and gender/age disparities. Utilizing data from the Shelter Support and Housing Administration division's Shelter Management Information System database, the research forecasts demand and provides critical insights: (1) geographic analysis identifies areas with the highest demand for shelter services, (2) demographic analysis uncovers gender and age-based disparities. These insights empower policymakers, shelter providers, and advocacy groups to allocate resources efficiently and proactively address homelessness challenges, ultimately preventing future hardships and tragedies."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
#| message: false
#| echo: false

#### Workspace set-up ####

#read in cleaned data #
cleaned_voter_statistics <- read.csv(here::here("inputs/data/cleaned_voter_statistics.csv"))
show_col_types = FALSE

#read in cleaned data #
summarized_voter_statistics <- read.csv(here::here("inputs/data/summarized_voter_statistics.csv"))
show_col_types = FALSE

#read in cleaned data #
summarized_voter_turnout <- read.csv(here::here("inputs/data/summarized_voter_turnout.csv"))
show_col_types = FALSE

#read in cleaned data #
finalized_voter_statistics <- read.csv(here::here("inputs/data/finalized_voter_statistics.csv"))
show_col_types = FALSE
```
